---
title: "Tuesday_25_5"
subtitle: "MARIO"
author: "Helena"
date: "5/25/2021"
output:
  html_document:
    toc: true
    toc_float: true
    theme: paper
    highlight: tango
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidytuesdayR)
library(gridExtra)
library(tidyverse)
library(bbplot)
library(tufte)
library(ggpomological)
library(hrbrthemes)
library(kableExtra)


library(wordcloud)

library(RColorBrewer)

library(wordcloud2)
```

## Loading the data
The simplest way is to use the ‘tt_load()’ function. This function accepts two types of inputs to determine which data to grab. It can be a date as a string in the YYYY-MM-DD format like below.

```{r read_data, include=TRUE}
data=tt_load("2021-05-25") 
drivers = data$drivers
records = data$records
# alternatively tt_data <- tt_load(2019, week=3)

readme(data) # to understand the data set
```

```{r explore, include = FALSE}

summary(drivers)
summary(records)
max(records$time)

```

## Some questions to explore

- How did the world records develop over time?
- Which track is the fastest?
- For which track did the world record improve the most?
- For how many tracks have shortcuts been discovered?
- When were shortcuts discovered?
- On which track does the shortcut save the most time?
- Which is the longest standing world record?
- Who is the player with the most world records?
- Who are recent players?

<center>**My aim today is to explore some new ggplot themes**</center>

-  bbplot package: https://github.com/bbc/bbplot/
- tvthemes package: https://ryo-n7.github.io/2019-05-16-introducing-tvthemes-package/
-  ggpomological  : https://www.garrickadenbuie.com/project/ggpomological/

```{r cool_themes_install}
#devtools::install_github("gadenbuie/ggpomological") 
#devtools::install_github('bbc/bbplot')
#remotes::install_github("hrbrmstr/hrbrthemes")
#devtools::install_github("Ryo-N7/tvthemes")
```
### How did the records develop over time & bbplot
```{r q1}
# time_period (y), date (x), grid by type
records_over_time<-ggplot(aes(x=date, y=time), data=records)+
   geom_jitter(size=0.5)+
   facet_wrap(vars(type))+
   bbc_style()

records_over_time

#bbplot::finalise_plot(plot_name = records_over_time,
#source = "Source: TidyTuesday",
#save_filepath = "21_05_25/images/records_over_time.png",
#width_pixels = 640,
#height_pixels = 550) # doesn't work

```
### Which track is the fastest?
```{r q2}

summary<-records %>% group_by(track, type) %>%
   summarise(mean=mean(time), min=min(time)) 

fastest_track<-summary %>%
   filter(min==min(summary$min))
fastest_average<-summary %>%
   filter(mean==min(summary$mean))


```
The fastest record is in the  `r fastest_track$track `, `r fastest_track$type` track. The record is currently at `r fastest_track$min` s. The average record time between `r min(records$date)` and `r max(records$date)` was on the `r fastest_average$track`, `r fastest_average$type` at `r fastest_average$time`.

### For which track did the world record improve the most?

```{r improvement}

summary_imp<-records%>%group_by(track, type)%>%
   summarise(min=min(time), max=max(time), dif=max-min,mean=mean(time), relative =dif/max )

max_improve <- summary_imp %>%
   filter(dif == max(summary_imp$dif))
max_rel_improve<-summary_imp %>%
   filter(relative==max(summary_imp$relative))
```

The highest absolute improvement was by `r max_improve$dif` in the `r max_improve$track`, `r max_improve$type`. However the biggest relative improvement was in the `r max_rel_improve$track`, `r max_rel_improve$type`, this improvement was `r round( max_rel_improve$dif, 2) `, which is `r round(max_rel_improve$relative * 100, 1) ` % of the original time.

###  On which track does the shortcut save the most time?

```{r shortcuts}

summary_shortcut<-records %>%
   group_by(track, shortcut)%>%
   summarise(n=n())
track_shortcut<-records %>%
   filter(shortcut == "Yes") %>%
   group_by(track) %>%
   summarise(n=n()) %>%
   nrow()

track_all<-records %>%
   group_by(track) %>%
   summarise(n=n()) %>%
   nrow()

track_list<-records%>%select(track)%>%
   unique()
   
```
Shortcut has been discovered on `r track_shortcut` out of `r track_all` tracks.

```{r shortcut by year, fig.width=8,fig.height=11, fig.align='left'}


ggplot(data=summary_shortcut, aes(x=track, y=n, fill=shortcut))+
   geom_col(position="dodge")+
     scale_x_discrete(labels = c(1:track_all))+
   theme_ipsum_pub()+
   scale_fill_viridis_d() #colorblind scale



ggplot(data=summary_shortcut, aes(x=shortcut, y=n, fill= shortcut))+
   geom_col(position="dodge")+
    labs(x="track", y="count",
       title="Shortcuts discovered",
       subtitle="",
       caption="by Helena Blackmore") +
   ylim(0,150)+
   theme_ipsum_ps()+
   facet_wrap(~track, scales="free")+
   scale_fill_ipsum()
  
```
```{r}
track_list%>% kable(align='l' )
```


###  When were shortcuts discovered?

```{r shortcuts_date}

records%>%
   group_by(track)%>%
   filter(shortcut=="Yes" & date==min(date))%>%
   select(track,date) %>%
  kableExtra::kable()

```
### On which track does the shortcut save the most time?

```{r, eval=FALSE}
# compare each track shortcut yes and shortcut no

shortcuts_dif<-records %>%
   group_by(track, shortcut, type)%>%
   filter(time==min(time))%>%
   select(track, type,shortcut,time)

time_saved <- function(track) 
{
 a3 = shortcuts_dif%>%filter(track=="track", type=="Three Lap", shortcut=="Yes")
 a1 = shortcuts_dif%>%filter(track=="track", type=="Single Lap", shortcut=="Yes")

 b3 =shortcuts_dif%>%filter(track==track, type=="Three Lap", shortcut=="No")
 b1 =shortcuts_dif%>%filter(track==track, type=="Single Lap", shortcut=="No")

 c3=b3$time-a3$time
 c1=b1$time-a1$time
 print(c(c3,c1))
 return(c(c3,c1))
}

time_saved(track="Rainbow Road")

alltracks=unique(shortcuts_dif$track)

for track in alltracks {
   
}

```
### Which is the longest standing world record?

```{r longest record}

longest_record<-records%>%
   filter(record_duration==max(record_duration))

longest_player<-drivers %>%
   filter(player==longest_record$player, year==max(year)) %>%
   select(position, total, nation)%>%
   kable(col.names =c("current leader position","world records", "nation"),
         caption="More about the longest record holder",
         digits=2,
         align="c")%>%
   kable_styling(latex_options="striped",
                 full_width = FALSE,
                 position = "float_left"
                 )
```
The duration ofthe longest world record was  `r longest_record$record_duration` days. Player `r longest_record$player` completed the `r longest_record$track`, `r longest_record$type` in `r  round(longest_record$time,2)` s on `r longest_record$system_played` on the `r longest_record$date`. 


`r longest_player`

###  Who is the player with the most world records?
```{r}
library(tvthemes)
import_simpsons()         ## "Akbar" font
import_theLastAirbender() ## "Slayer" font
import_rickAndMorty()     ## "Get Schwifty" font
import_roboto_condensed() ## "Roboto Condensed" Google Font import from hrbrthemes
import_titillium_web()    ## "Titillium Web" Google Font import from hrbrthemes
import_spongeBob()        ## "Some Time Later" font
import_cinzel()           ## "Cinzel" font to use with 'The Palettes of Ice & Fire'

#install.packages("extrafont")
library(extrafont)
loadfonts() ## You need to do this at the beginning of a session.
```

```{r}
most_records<-drivers%>%
   filter(total==max(total) & year==max(year))%>%
   select(position, total, nation)%>%
   kable(col.names =c("current leader position","world records", "nation"),
         caption="More about the holder of most world records",
         digits=2,
         align="c")%>%
   kable_styling(latex_options="striped",
                 full_width = FALSE,
                 position = "float_left"
                 )

top_drivers<-drivers%>%
   filter(total>=50 )%>%
   mutate(total = sort(total))

top_drivers%>%
  mutate(player = fct_reorder(player, total, .fun='median')) %>%
  ggplot( aes(x=reorder(player, total), y=total))+
   geom_point()+
   labs(title = "Top Record Holders",
       caption = glue::glue("
                      TidyTuesday"),
       x = "player name",
       y = "no. of world records") +
   theme_simpsons(title.font = "Akbar",
                 text.font = "Akbar",
                 axis.text.size = 6)+
   scale_y_continuous(trans='pseudo_log')
   
```

###  Who are recent players?

```{r recent players}

recent_players<-drivers%>%
   filter(year>= 2015)%>%
   group_by(player)%>%
   summarise(n=n())


```

```{r wordcloud1, fig.align='left', fig.cap="Players active since 2015"}
set.seed(1234) # for reproducibility 
wordcloud(words = recent_players$player, freq = recent_players$n, min.freq = 1,           max.words=200, random.order=FALSE, rot.per=0.0001,colors=brewer.pal(8, "Dark2"), scale=c(0.9,0.25))
```
```{r wordcloud2, fig.align='right', fig.cap= "Players active from 2015"}
wordcloud2(data=recent_players, size=0.1, color='random-dark')
```



